% Original author:
% Trey Hunner (http://www.treyhunner.com/)

\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{graphicx}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\scaledfaExternalLink}{\raisebox{0.1\height}{\scalebox{0.7}{\faExternalLink*}}}

\name{Wyatt Avilla}
\address{(408)506-2189}
\address{\href{mailto:wyattmurphy1@gmail.com}{wyattmurphy1@gmail.com}}
\address{\href{https://github.com/wyatt-avilla}{github.com/wyatt-avilla \scaledfaExternalLink} }

\begin{document}

\begin{rSection}{Education}

	\textbf{University of California, Santa Cruz} \hfill \textit{September 2021 - Present} \\
	\textit{Major:} B.S. Cognitive Science, specializing in AI \& HCI \hfill \textbf{CGPA: 3.9}\\
	\textit{Minor:} Computer Science

\end{rSection}

\begin{rSection}{Technical Strengths}

	\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
		Programming Languages & C/C++, Python, Rust, Bash, Lua                               \\
		Software \& Tools     & Git, Linux, GitHub Actions, Pandas, WebAssembly, Docker, AWS \\
	\end{tabular}

\end{rSection}

\begin{rSection}{Work Experience}

	\begin{rSubsection}{Data Structures \& Algorithms Tutor}{July 2024 - September 2024}{University of California, Santa Cruz}{}
		\item Assisted students in understanding core concepts of data structures and algorithms.
		\item Led and conducted group sessions to facilitate collaborative learning and peer discussions.
		\item Developed supplemental materials to enhance students' learning experiences.
		\item Helped students prepare for exams by reviewing key topics and solving practice problems.
	\end{rSubsection}

\end{rSection}

\begin{rSection}{Relevant Courses}
	\itab{\textbf{Core Courses}} \tab{}  \tab{\textbf{Other Courses}}
	\\ \itab{Data Structures \& Algorithms } \tab{}  \tab{Discrete Mathematics}
	\\ \itab{Object Oriented Programming} \tab{}  \tab{Linear Algebra}
	\\ \itab{Parallel Programming} \tab{}  \tab{Vector Calculus}
	\\ \itab{Computer Systems} \tab{} \tab{}

\end{rSection}

\begin{rSection}{Projects}

	\item {\bf \href{https://github.com/search?q=repo%3Adoldecomp%2Fmelee++author%3Awyatt-avilla&type=pullrequests&ref=advsearch}{PowerPC Assembly Reverse Engineering \scaledfaExternalLink}} {\hfill March 2024} \\
	Contributed to an open-source reverse engineering project for Super Smash Bros. Melee on the Nintendo GameCube. Focused on analyzing PowerPC assembly code and translating it into C. Actively collaborated with a team of developers to improve accuracy and functionality, contributing to a collective effort to document and recover the game's codebase.

	\item {\bf \href{https://github.com/wyatt-avilla/feframe}{Rust-Based Website \scaledfaExternalLink}} {\hfill June 2024} \\
	Developed a fully Rust-based website leveraging WebAssembly and Trunk for building, hosted on shuttle.rs. Utilized Rust's procedural macros to dynamically generate HTML and CSS, ensuring a strongly-typed, efficient development process without relying on traditional frontend languages.

	\item {\bf \href{https://github.com/wyatt-avilla/discord-tiktok-tts-bot}{Discord Bot \scaledfaExternalLink}} {\hfill March 2023} \\
	Developed a Discord bot utilizing the TikTok text-to-speech API to enable real-time text-to-speech requests within voice channels. The bot allows users to submit text messages which are then converted to speech and played back live during voice calls.


\end{rSection}

\end{document}
